\documentclass[11pt,a4paper]{article}

% Packages for formatting
\usepackage[margin=0.75in]{geometry} % Clean, modern margins
\usepackage{titlesec}                % Custom section formatting
\usepackage{enumitem}                % Better list formatting
\usepackage{hyperref}                % Clickable links
\usepackage{xcolor}                  % Color customization

% Color definitions for links
\definecolor{linkcolor}{RGB}{0, 80, 160}
\hypersetup{
    colorlinks=true,
    linkcolor=linkcolor,
    filecolor=linkcolor,      
    urlcolor=linkcolor,
}

% Customizing section titles
\titleformat{\section}
  {\Large\bfseries\uppercase} % Format
  {}                          % Label
  {0em}                       % Sep
  {}                          % Before-code
  [\vspace{-0.5em}\rule{\textwidth}{0.4pt}] % Horizontal line after

\titlespacing*{\section}{0pt}{1.5ex plus 1ex minus .2ex}{1ex plus .2ex}

% Removing page numbers
\pagestyle{empty}

\begin{document}

% --- HEADER ---
\begin{center}
    {\Huge \textbf{Jai Verma}}\\[0.5em]
    Invalidenstr. 100, 10115 Berlin, Germany \\
    \href{mailto:vermajai335@gmail.com}{vermajai335@gmail.com} \,|\, 
    017670906622 \\[0.5em]
    \textbf{Portfolio:} \href{https://jaiv5459-gif.github.io/Portfolio/}{jaiv5459-gif.github.io/Portfolio} \,|\,
    \textbf{GitHub:} \href{https://github.com/jaiv5459-gif}{jaiv5459-gif}
\end{center}
\vspace{1em}

% --- CAREER OBJECTIVE ---
\section*{Career Objective}
An aspiring Software Engineer actively seeking a working student position. Highly motivated to continuously develop technical skills, apply academic computer science principles to real-world applications, and contribute meaningfully to innovative projects.

% --- EDUCATION ---
\section*{Education}
\noindent
\textbf{Bachelor of Computer Science} \hfill \textit{Currently Studying} \\
GISMA University of Applied Sciences \hfill Berlin, Germany

% --- TECHNICAL SKILLS ---
\section*{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={--}, itemsep=2pt]
    \item \textbf{Programming \& Scripting:} Python, JavaScript, PHP, SQL
    \item \textbf{Web Development:} HTML, CSS, 3-Tier Web Architecture
    \item \textbf{Databases \& Architecture:} MySQL, Relational Database Design, SQL Normalization
    \item \textbf{Tools \& Technologies:} Git/GitHub (Version Control), LaTeX (Documentation), WebDrivers (Selenium), VS Code
    \item \textbf{Operating Systems:} Linux, Windows
\end{itemize}

% --- ACADEMIC PROJECTS ---
\section*{Academic Projects}

\noindent
\textbf{Computer Science Portfolio Website} \hfill \textit{HTML, CSS, JS, LaTeX}
\begin{itemize}[leftmargin=0.15in, label={--}, itemsep=1pt, topsep=2pt]
    \item Designed, structured, and deployed a professional computer science portfolio hosted on GitHub Pages utilizing a modern Bento-box UI.
    \item Maintained a well-documented GitHub repository featuring technical exercises and a LaTeX-generated CV.
\end{itemize}

\vspace{0.5em}
\noindent
\textbf{Project Oceanus: Fleet Management Simulation} \hfill \textit{PHP, MySQL, JavaScript}
\begin{itemize}[leftmargin=0.15in, label={--}, itemsep=1pt, topsep=2pt]
    \item Developed a 3-tier web-based game application focused on fleet management.
    \item Successfully engineered database connections, managed CRUD operations, and designed the front-end layout for seamless user interaction via asynchronous API calls.
\end{itemize}

\vspace{0.5em}
\noindent
\textbf{Lantern Library Database System} \hfill \textit{SQL, Database Architecture}
\begin{itemize}[leftmargin=0.15in, label={--}, itemsep=1pt, topsep=2pt]
    \item Designed and implemented a highly normalized (3NF) relational database architecture for a library events booking system.
    \item Created detailed ERD models and executed complex SQL table scripts to ensure data integrity without redundancy.
\end{itemize}

% --- GENERAL & SOFT SKILLS ---
\section*{Soft Skills \& Languages}
\begin{itemize}[leftmargin=0.15in, label={--}, itemsep=2pt]
    \item \textbf{Languages:} German, English
    \item \textbf{Professional Traits:} Analytical Problem Solving, Technical Documentation, Adaptability, Concept Tree Learning (breaking down complex domains into structured hierarchies), Team Collaboration.
\end{itemize}

% --- PROFESSIONAL EXPERIENCE ---
\section*{Professional Experience}
\noindent
Currently seeking working student opportunities to gain hands-on professional experience in software engineering and systems development.

% --- DECLARATION ---
\section*{Declaration}
\noindent
I hereby declare that the above-mentioned statements are true and correct to the best of my knowledge and belief.\\[2em]
\noindent
\textbf{Jai Verma} \\
\textit{Berlin, Germany}

\end{document}